Target Markdown

### 2023-10-13 _targets.Rmd
Add sem total effect for simplified sem

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + rho, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_coeff, {
    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti
    }),
  tar_target(sem_simplified_collinearity,
    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

@@

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = c(
              "rho" = 0,
              "env_stoch" = .1,
              "ct_alive" = .2,
              "avg_int_strength" = .01,
              "h" = 2,
              "w_avg_tlvl" = 1.5,
              "Z" = 100
            )
          )
        }
        )
    ) %>%
    select(-fix_effect, -values)
  )
)
```

@@

```{r}
tar_load(fix_fw_stab)
tar_load(fix_fw_stab_comp)

>>>>

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + rho, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_coeff, {
    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti
    }),
  tar_target(sem_simplified_collinearity,
    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(sem_simplified_eff_file, here::here("data", "sem_simplified_eff"), format = "file"),
  tar_target(sem_simplified_eff, {
    readRDS(sem_simplified_eff_file)
    #semEff(sem_simplified, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

@@

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = c(
              "rho" = 0,
              "env_stoch" = .1,
              "ct_alive" = .2,
              "avg_int_strength" = .01,
              "h" = 2,
              "w_avg_tlvl" = 1.5,
              "Z" = 100
            )
          )
        }
        )
    ) %>%
    select(-fix_effect, -values)
  ),
  tar_target(pred_stab_comp_rho_tbl,
  pred_stab_comp_rho %>%
  select(-variable) %>%
  mutate(slope = map(slope,
      ~pivot_longer(.x,
        -c(rho, slope),
        names_to = "variable",
        values_to = "variable_values"
      )
    )
  ) %>%
  unnest(cols = slope)

  )
)
```

@@

```{r}
tar_load(fix_fw_stab)
tar_load(fix_fw_stab_comp)
tar_load(pred_stab_comp_rho)
```

```{r}
tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      x = predictor,
      y = effect,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(cols = vars(response)) +
  labs(x = "Predictor", y = "Total effect") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r}
cols <- c("Community stability" = "black", "Asynchrony" = "blue", "Population stability" = "darkgreen")
alpha <- c("Community stability" = 1, "Asynchrony" = .3, "Population stability" = .3)

p_sem_tot_stab <- tar_read(sem_simplified_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("rho", "env_stoch","cpe", "sae_total", "evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async", "S", "ct")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      y = predictor,
      x = effect,
      color = response,
      alpha = response,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  scale_colour_manual(values = cols) +
  scale_alpha_manual(values = alpha) +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  #facet_grid(cols = vars(response)) +
  labs(
    x = "Total standardised effect",
    color = "Stability component",
    alpha = "Stability component"
    ) +
  theme_bw() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.justification = "right"
  )
ggsave_multiple(
  paste0("p_sem_tot_stab", c(".png", ".pdf")),
  plot = p_sem_tot_stab,
  path = here::here("report", "figures"),
  scale = 1.8,
  dpi = 400,
  width = 80,
  height = 80 * 1.1,
  units = "mm")
```

```{r}
tar_load(pred_stab_comp_rho_tbl)
p_pred_stab_comp_rho <-
  pred_stab_comp_rho_tbl %>%
  mutate(
    response = var_replacement()[response],
    variable = var_replacement()[variable],
    ) %>%
  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Food-web structure",
    fill = "Slope Stability-Richness"
    ) +
  theme_bw() +
  theme(legend.position = "bottom")
ggsave_multiple(
  paste0("p_pred_stab_comp_rho", c(".png", ".pdf")),
  plot = p_pred_stab_comp_rho,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 80,
  height = 80 * 1.1,
  units = "mm")
```
